Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-04-17 draft/paper1.tex
Intro: accreted fraction

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies and a large fraction of these massive progenitors become quiescent 
    at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase in the ``two-phase'' formation scenario is driven by 
    non-dissipative processes such as dry mergers with other galaxies 
    (e.g. \citealt{Naab2006, Khochfar2006}). 
    According to the ``two-phase'' scenario, minor mergers drive the growth of massive 
    galaxies at late times and can help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the build-up 
    of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).        
    {\bf Words here about mass dependence: in the simulations, a larger fraction of the mass 
    is ex-situ at increasingly higher mass. Seen in early work by Naab, Oser, etc, and in the 
    Illustris papers. First prediction to compare with is that the accreted/ex-situ fraction is 
    a function of mass.}

>>>>

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies and a large fraction of these massive progenitors become 
    quiescent at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase in the ``two-phase'' formation scenario is driven by 
    non-dissipative processes such as dry mergers with other galaxies 
    (e.g. \citealt{Naab2006, Khochfar2006}). 
    According to the ``two-phase'' scenario, minor mergers drive the growth of 
    massive galaxies at late times and can help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the 
    build-up of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, 
    Patel2013}).        
    \update{
    More importantly, both numerical simulation (e.g. \citealt{Oser2010}) and 
    semi-analytic model (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction of the accreted component should increase with total stellar mass, 
    although different models still predict somewhat different values at fixed 
    stellar mass (e.g. \citealt{Lackner2012, Cooper13, Qu2017}).
    According to the recent results from Illustris \footnote{
    \texttt{http://www.illustris-project.org/}} simulation (\citealt{Vogelsberger2014},
    \citealt{Genel2014}), the fraction of the accreted mass increases significantly
    with total stellar mass at \logms{}$>11.0$, and the accreted component starts 
    to dominate the stellar mass budget ($f_{\mathrm{accreted}}>0.5$) at 
    \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
    }

    \update{
    These predictions

    }
    \song{The following section focuses on the environmental dependence, should move 
    to Paper II, I will replace it with introduction that focus on the mass
    dependence and outskirt profile.}
